\documentclass[11pt]{article}

% ---- packages (kept close to a standard preprint) ----
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{enumitem}
\usepackage{xcolor}
\definecolor{linkblue}{HTML}{1A4FA0}
\usepackage[colorlinks=true, linkcolor=linkblue, urlcolor=linkblue, citecolor=linkblue]{hyperref}

% ---- theorem environments (match the paper) ----
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{principle}{Principle}

% ---- helpers ----
\newcommand{\repo}[1]{\href{https://github.com/dm3n/#1}{\texttt{github.com/dm3n/#1}}}
\setlist[itemize]{itemsep=2pt, topsep=3pt, leftmargin=1.4em}

\title{\textbf{Architecting Agentic Software Systems}\\[2pt]
\large A Technical Portfolio and Professional Itinerary}
\author{Daniel Ray Edgar\\[2pt]
\normalsize \href{mailto:daniel@nodebase.ca}{daniel@nodebase.ca} \quad\textbar\quad
\href{https://github.com/dm3n}{github.com/dm3n} \quad\textbar\quad
\href{https://finsider.ai}{finsider.ai}}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
\noindent
This document is a technical overview of my work designing, building, and deploying
\emph{agentic software systems}: autonomous and semi-autonomous programs that plan,
act, and verify their own work under engineered constraints. I am the Chief Technology
Officer of Finsider, where I built and deployed \textsc{Symphony}, a supervised-autonomy
software-delivery runner that drives product tickets to reviewed, evidence-backed pull
requests. Before this I studied Computer Science at Queen's University, then raised
\$220{,}000 at a \$2.2M valuation as co-founder and CEO of an Antler Canada--backed company
at the age of 19, and authored single-author research formalizing the reliability of
multi-step language-model reasoning, validated against four frontier models to within
roughly one percent of empirical accuracy. A second single-author paper, \emph{The
Information-Maintenance Hypothesis}, argues that aging, intelligence, and markets are the
same problem in information theory. The unifying thread of this portfolio is a
specific, defensible engineering thesis about autonomous AI, derived from that research and
realized in production. This document doubles as a professional itinerary; my curriculum
vitae is appended. Every system referenced is hyperlinked to its public source repository.
\end{abstract}

% =====================================================================
\section{Introduction}
% =====================================================================
I build artificial-intelligence systems for the highest-stakes work in finance, and I build
the autonomous infrastructure that builds them. My work spans three layers that most
engineers treat separately: the \emph{theory} of why language-model systems fail, the
\emph{systems} that exploit that theory in production, and the \emph{tooling} that lets a
single engineer operate at the throughput of a team.

The defining specialization is \emph{agentic software}: programs that decompose a goal
into steps, take real actions in the world (writing code, querying corpora, operating a
browser, transacting), and judge the quality of their own output. Agentic systems are
powerful and notoriously unreliable; the central engineering problem is making them
trustworthy enough to point at production. The systems in this portfolio are my answers to
that problem, and Section~\ref{sec:research} gives the formal reason they are designed the
way they are.

\paragraph{Selected facts.}
Chief Technology Officer of Finsider on a \$200{,}000 salary at the age of 20; raised
\$220{,}000 at a \$2.2M valuation (Antler Canada Fund~I SAFE) as co-founder/CEO before
turning 20; single-author research validated against GPT-5, Claude Opus~4.6, Claude
Sonnet~4.6, and Gemini~3.1~Pro; author of \textsc{Symphony}, deployed live in a commercial
engineering environment.

% =====================================================================
\section{Core Technical Competencies}
% =====================================================================
\noindent
\begin{description}[leftmargin=0pt, labelsep=0.5em, style=unboxed, itemsep=4pt]
  \item[\normalfont\textbf{Agentic systems (primary specialization).}] Supervised-autonomy
  architectures; ticket-native state machines; acceptance-contract prompting; evidence-gated
  delivery pipelines; multi-agent orchestration with shared context; tool-use design;
  process supervision, watchdogs, and safe automated Git; failure recovery with bounded
  retry.
  \item[\normalfont\textbf{Applied AI / LLMs.}] LLM orchestration; Retrieval-Augmented
  Generation (Vertex AI RAG; corpus-per-workload; parallel multi-query retrieval with
  dedup/ranking); structured extraction with calibrated confidence; process reward models;
  frontier-model evaluation; Anthropic, Google Vertex AI, and Gemini~2.0~Flash APIs.
  \item[\normalfont\textbf{Languages.}] Python, TypeScript/JavaScript, Swift (iOS), SQL,
  Bash, \LaTeX.
  \item[\normalfont\textbf{Full-stack.}] Next.js~16, React~19, Tailwind~v4, shadcn/ui;
  Supabase (PostgreSQL, Row-Level Security, Auth, Storage), Firebase, Sanity (headless CMS);
  Stripe, Resend, Twilio; server-sent-event streaming, async job queues, webhook pipelines.
  \item[\normalfont\textbf{Cloud \& infrastructure.}] Google Cloud Platform (Compute Engine,
  Cloud Storage, Vertex AI), Vercel; self-hosted Proxmox cluster, Docker, \texttt{systemd},
  macOS \texttt{launchd}, Tailscale; CI-aware multi-repository delivery.
  \item[\normalfont\textbf{Applied mathematics.}] Probability theory; Bernoulli and
  Hoeffding bounds; maximum-likelihood estimation; the delta method and confidence-interval
  construction; empirical model evaluation.
  \item[\normalfont\textbf{Financial domains.}] M\&A Quality of Earnings; Canadian mortgage
  underwriting (GDS/TDS, OSFI guidelines, stress testing); financial-document AI;
  document-authenticity and fraud-signal detection.
\end{description}

% =====================================================================
\section{Research Foundations: The Reliability of Agentic Reasoning}
\label{sec:research}
% =====================================================================
The design of every agentic system I build follows from a result I proved in
\emph{Uncertainty Propagation in Tree-Structured Language Model Reasoning}
(\repo{uncertainty-propagation}). Model each step of an autonomous process as a Bernoulli
trial with step-specific failure probability $\theta_i$.

\begin{theorem}[Chain success]
For an $n$-step reasoning chain $\mathcal{C}_n$ with conditionally independent steps,
\[
  \mathbb{P}(\textsc{correct}\mid \mathcal{C}_n,\boldsymbol{\theta}) \;=\; \prod_{i=1}^{n}(1-\theta_i).
\]
\end{theorem}

\begin{corollary}[Exponential decay]
With mean failure rate $\bar\theta$, $\;\mathbb{P}(\textsc{correct}) \le (1-\bar\theta)^n \le e^{-n\bar\theta}$.
\end{corollary}

The practical consequence is severe: a long, unsupervised agent run decays exponentially in
reliability, so it \emph{cannot} be trusted to ship. The paper further proves that a
$k$-ary, depth-$d$ \emph{tree} with majority aggregation decays only sub-exponentially in
total compute, $\exp(-\Omega(N^{1-1/(d+1)}))$, and derives the compute-optimal branching
factor and depth, together with maximum-likelihood estimators and delta-method confidence
intervals for end-to-end success. Empirically, the model predicts observed accuracy to
within $\sim$1\% across GPT-5, Claude Opus~4.6, Claude Sonnet~4.6, and Gemini~3.1~Pro; at a
fixed $48$-step budget a chain succeeds $\approx 0.2\%$ of the time while a depth-3 tree
succeeds $97.9\%$.

This yields the engineering principle that organizes the rest of this portfolio.

\begin{principle}[Supervised, tree-structured autonomy]
Do not ship from one long autonomous chain. Decompose work into short, independently
verified units; aggregate across them with explicit checkpoints (validation, evidence,
human review). Keep per-step failure low and let aggregation, not chain length, carry
reliability.
\end{principle}

% =====================================================================
\section{\textsc{Symphony}: A Supervised-Autonomy Delivery System}
% =====================================================================
\textsc{Symphony} (\repo{symphony}) is the clearest demonstration of my agentic-software
engineering. It is a Jira-native, evidence-gated runner that takes a product ticket from
backlog to a reviewed, evidence-backed pull request, with a human as the sole approval
authority. I designed and built it as CTO of Finsider, where it runs live against a
multi-repository codebase. It is a $\sim$2{,}300-line, standard-library Python orchestrator
(no agent framework) chosen for auditability and portability.

\paragraph{Architecture.} The system treats the coding agent as a capable but unprivileged
developer: it may implement, validate, and produce evidence, but never holds approval
authority. Its defining properties:
\begin{itemize}
  \item \textbf{Jira as the state machine.} Ticket status and labels \emph{are} the control
  flow; there is no external queue or database. Because state is re-derived from Jira on
  every poll, the daemon is crash-safe and losslessly resumable, a direct application of
  the ``keep each step verifiable'' principle.
  \item \textbf{Per-ticket isolation.} Each ticket runs in an isolated Git workspace on its
  own branch, with pinned commit identity and evidence excluded from history.
  \item \textbf{Acceptance contracts.} Acceptance criteria are parsed from the ticket and
  injected into the agent prompt as an explicit verification checklist.
  \item \textbf{Evidence gating.} No ticket reaches review, and no pull request is created,
  without \textsc{Playwright}-captured screenshots/video of the running result, integrity-
  checked against minimum-size thresholds to reject empty or synthetic ``evidence.''
  \item \textbf{Intent-classified human review.} Reviewer comments are classified
  (question vs.\ rework vs.\ approval vs.\ neutral), so the loop answers questions in place
  and re-runs the agent only on genuine change requests.
  \item \textbf{Cross-repo scope critic.} The system detects when a ticket requires changes
  across multiple repositories and blocks review if coverage is incomplete.
  \item \textbf{Safety by construction.} \texttt{-{}-force-with-lease} only; recursive
  process-tree cleanup and a dev-server watchdog; bounded failure auto-retry with cooldown;
  a single-instance file lock.
  \item \textbf{Two deployment targets.} macOS \texttt{launchd} for local operation and an
  always-on GCP Compute Engine VM under \texttt{systemd} for production.
\end{itemize}

\paragraph{The invariant.} The controls compose to a single guarantee: \textsc{Symphony}
can never merge code, never force-clobber a branch, never advance unverified work, and never
fail silently. The maximum blast radius of any malfunction is a clearly labeled, un-merged
draft pull request plus a notification, exactly the property required of an autonomous
system pointed at production. The full engineering record (architecture, state machine,
hardening, deployment, security, and sanitized reference interfaces) is published at
\repo{symphony}.

% =====================================================================
\section{A Portfolio of Agentic and AI Systems}
% =====================================================================

\paragraph{Airbank: Quality-of-Earnings engine
(\repo{airbank}).} An eleven-section, RAG-grounded extraction pipeline that produces
analyst-grade M\&A Quality-of-Earnings workbooks in which every figure is traceable to a
source document. It applies Principle~1 to document AI: rather than one long extraction
pass, each section is an independently verified unit with calibrated confidence, audit-grade
citation (document, page, verbatim excerpt), and a policy of flagging missing data rather
than fabricating it; a deterministic path bypasses retrieval for clean spreadsheets, and a
formula resolver reconciles cross-section dependencies over a live SSE stream.

\paragraph{Airbank: mortgage underwriting
(\repo{airbank-mortgage-platform}).} Full-lifecycle AI origination for Canadian brokers:
Canadian-specific document extraction (T4, NOA, pay-stub, LOE); \emph{fraud-signal
detection} via PDF-metadata, font-consistency, and name/income cross-checks; a GDS/TDS
engine with stress-test rate; one-call intake orchestration; real-time upload verification;
and an autonomous, cron-driven pipeline agent that generates role-aware priorities across a
live deal pipeline.

\paragraph{Macintosh: a multi-agent engineering operating system
(\repo{macintosh}).} A reproducible, self-hosted environment that lets one engineer ship
like a team: a six-stage agentic coding pipeline expressed as Claude Code skills; four
coding agents (Claude Code, Codex, Gemini, OpenCode) sharing one context; a Personal
Knowledge Brain (Obsidian + an LLM compiler) for persistent memory; and a Proxmox/Docker
homelab with a human-gated approval model.

\paragraph{VisionClaw: a real-time multimodal agent
(\repo{VisionClaw}).} An accessibility-first iOS agent (Swift/SwiftUI, Meta Wearables DAT
SDK, Gemini Live over WebSocket) that streams video from Meta Ray-Ban glasses and
proactively narrates the world for visually impaired users, with hands-free activation and
resilient session recovery.

\paragraph{The Information-Maintenance Hypothesis: a second research paper
(\repo{information-maintenance-hypothesis}).} A single-author theory paper arguing that
three problems, why organisms age, what intelligence is, and how markets price the world,
are one problem: maintaining a low-entropy predictive model against entropy at a
free-energy cost. It is anchored on two results that are theorems rather than analogies,
Landauer's principle (maintaining a bit of information costs at least $k_{\mathrm B}T\ln 2$
of energy) and the Kelly--Cover identity (capital growth rate equals mutual information with
the future), and it closes with eleven falsifiable predictions across biology, AI, and
finance. Written in \LaTeX{} with four figures and three appendices, it demonstrates the
same first-principles modeling, from formal definition to proven result, that underwrites
the engineering thesis above.

\paragraph{Further systems.} \textbf{ROGI} (\repo{rogi}), an AI-native mortgage-intake
funnel with a Canadian qualification engine (first version sold for \$7{,}500);
\textbf{Sacred Secretion Agent} (\repo{sacred-secretion-agent}), a fully autonomous
scheduling/email agent; \textbf{Nassau} (\repo{nassau}), a complete e-commerce platform
built from scratch (Next.js, Sanity CMS, Stripe, Firebase); and a second research
manuscript (\repo{human-divinity}).

% =====================================================================
\section{Itinerary: Roles, Milestones, and Technical Objectives}
% =====================================================================
\noindent\emph{Primary location of work: Toronto, Ontario, Canada (Antler Canada / OneEleven,
325 Front St W).}

\subsection{Co-founder \& CEO: Flagpost AI Inc.\ (Sep 2025 -- Q1 2026)}
\begin{itemize}
  \item Selected into the Antler Canada TOR8 residency (commenced Sep 2025) and passed the
  Antler Investment Committee.
  \item \textit{Funding milestone:} raised \$220{,}000 at a \$2.2M valuation via a SAFE from
  Antler Canada Fund~I, L.P.; incorporated Flagpost AI Inc.\ (Nov 2025).
  \item \textit{Duties:} company formation, team and cap-table structure, product direction
  (AI-native sell-side M\&A preparation), and investor relations.
  \item \textit{Outcome:} stepped aside to pursue the broader M\&A-intelligence thesis.
\end{itemize}

\subsection{Founder: Airbank (Q1 2026)}
\begin{itemize}
  \item \textit{Technical objectives:} design an AI-native operating system for M\&A,
  beginning with the Quality-of-Earnings wedge; build the QoE and mortgage platforms above.
  \item \textit{Development phases:} RAG ingestion $\rightarrow$ section-wise extraction with
  confidence flags $\rightarrow$ auditable source-linked cells $\rightarrow$
  reconciliation/export; mortgage intake $\rightarrow$ AI verification $\rightarrow$
  underwriting audit $\rightarrow$ pipeline orchestration.
  \item \textit{Customer acquisition:} signed LOIs, NDAs, and advisory agreements with
  senior professionals across private credit, M\&A advisory, investment banking, and private
  equity.
\end{itemize}

\subsection{Chief Technology Officer: Finsider (2026 -- Present)}
\begin{itemize}
  \item \textit{Compensation:} \$200{,}000 annual salary, materially above the norm for
  the role and tenure.
  \item \textit{Technical objectives:} automate Quality of Earnings end-to-end; own the
  multi-repository platform (frontend, backend engine, AI/agent services) and the
  financial-correctness layer (Balance Sheet, P\&L, Cash Flow, and Cash Proof tie-out with
  standardized export).
  \item \textit{Signature deliverable:} designed and deployed \textsc{Symphony} as the
  company's agentic delivery infrastructure.
  \item \textit{Forward plan (petition period):} (i)~harden and scale the QoE automation and
  agentic delivery pipeline; (ii)~extend financial-statement correctness and export
  coverage; (iii)~grow enterprise adoption of the automated QoE product; (iv)~advance the
  supervised-autonomy research-to-production loop.
\end{itemize}

% =====================================================================
\section{Education}
% =====================================================================
\textbf{Queen's University}, Computer Science. Left to build full-time after raising
venture funding.

% =====================================================================
\section*{Repository Index}
\addcontentsline{toc}{section}{Repository Index}
% =====================================================================
\begin{itemize}
  \item \textbf{Portfolio (this overview):} \repo{portfolio}
  \item \textbf{\textsc{Symphony}:} \repo{symphony}
  \item \textbf{Macintosh (engineering OS):} \repo{macintosh}
  \item \textbf{Research, reasoning reliability:} \repo{uncertainty-propagation}
  \item \textbf{Research, information-maintenance hypothesis:} \repo{information-maintenance-hypothesis}
  \item \textbf{Research, manuscript:} \repo{human-divinity}
  \item \textbf{Airbank QoE} (private)\textbf{:} \repo{airbank}
  \item \textbf{Airbank Mortgage} (private)\textbf{:} \repo{airbank-mortgage-platform}
  \item \textbf{ROGI:} \repo{rogi} \;\textbar\; \repo{rogi-v2}
  \item \textbf{VisionClaw:} \repo{VisionClaw}
  \item \textbf{Nassau:} \repo{nassau}
  \item \textbf{Sacred Secretion Agent:} \repo{sacred-secretion-agent}
  \item \textbf{Other:} \repo{nodebase} \;\textbar\; \repo{ratestore} \;\textbar\; \repo{OpenCV}
\end{itemize}

\vspace{6pt}
\noindent\footnotesize\textit{Prepared \today. Curriculum vitae appended. Sensitive investor,
customer, and financial specifics are maintained in a private data room available on request.}

\end{document}
